Containers and R: the Rockerverse and beyond

### 2019-09-09 manuscript.Rmd
add outline for author contribution section

>>>>

## Author contributions

DN conceived of the presented idea and \href{https://github.com/nuest/rockerverse-paper/issues/3}{initialised the formation of the writing team}.
CB ..
RC ..
DE ..
ME ..
CF ..
BW ..
KR ..
NR ..
NX ..
LS \& NT wrote the section on Bioconductor.
All authors contributed to the discussion and outlook section and approved the final version.
This articles was collaboratively written at \href{https://github.com/nuest/rockerverse-paper/}{https://github.com/nuest/rockerverse-paper/}.
The \href{https://github.com/nuest/rockerverse-paper/graphs/contributors}{contributors page} and \href{https://github.com/nuest/rockerverse-paper/commits/master}{commit history} provide a detailed view on the respective contributions.
